\Title

### 2022-09-29 Grimaldi-etal-BiolCybernetics.tex
Results: 3.1

\subsection{Task definition: fast motion detection}
%%%-----------------------------------------------------------------
\note{c'est la meme expe faite par baudot et modelisée par kremkow}
Let us now define a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the field of vision. In animals with a fovea, this is particularly useful as it allows to move the area with the highest density of photoreceptors in the environment, for example at a point of interest. For example, saccades are rapid movements of the eyeball that reposition the center of vision. In humans, these are very frequent (on average one every 3 per second~\citep{dandekar_neural_2012}). They are produced very rapidly (about $80~\ms$) and display a whole range of speeds. At a more microscopic scale, the human gaze moves with an incessant drift similar to a Brownian-like trajectory~\citep{poletti_head-eye_2015}. To maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}. This approach first defines a finite set of possible 2D motions in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set of eye movements as the Cartesian product of N-V-phi=8 linearly spaced motion directions and N-Y-velocity=7 different velocities (see inset of \seeFig{motion_task}-(a)). Note that the velocities are sampled on a geometric scale between $1/4$ and $v-speed_base = 4$. Next, we define one trajectory of gaze as segments whose duration is drawn from a Poisson distribution with an average block length = $20~\ms$ - similar to a Lévy flight~\citep[p. 289]{mandelbrot_fractal_1982}. Finally, the trajectory is integrated by assuming 1/ that velocities are uniformly and independently sampled from the set of different motion-sets and 2/ that motion is uniform during a time segment. The resulting instances yield trajectories qualitatively similar to those observed for human eye movements (\seeFig{motion_task}-(a)).

@@

%
Finally, the output of the MLR model is an event-based representation predicting at each position and at each time the probability of each motion. Such an output gives a form of optical flow that can be exploited for non-rigid motions, but we have defined here, for simplicity, an evaluation method that applies to our task with a full field motion. We have shown above that when different independent observations (here, the estimated motion at different spatial locations) are recognized as having a common cause (here, the rigid motion of the image), then an optimal estimate of the logit of this probability is the sum of the logits of the independent probabilities. By taking the logit of the probability of the output given by the model, we can therefore calculate the probability of the output. This allows one to calculate the accuracy (as the percentage of times the motion is accurately predicted) or the squared error $|| \speed - ||^2$ of the velocity estimate given by :
$
\speed = \sum_{\class} \speed_\class \cdot Pr(\class \vert image)
$ 
These calculations are performed on a different input dataset than the one used in the training or validation steps. These metrics will be useful to compare our methods with other methods on our defined task.  The complete code to reproduce the results of this paper is available at \url{https://github.com/SpikeAI/pyTERtorch}.  
%
\section{Results}
\label{sec:results}
%%%-----------------------------------------------------------------
%: fig:kernels
%%%-----------------------------------------------------------------
\subsection{Kernels learned for motion detection}
%%%-----------------------------------------------------------------
\begin{figure*}[ht!]
    {\centering
    %\vspace{-3cm}
    \includegraphics[width=\linewidth]{figures/motion_kernels.pdf}
    }
    %\vspace{-.5cm}
    \caption{
    	Representation of the weights for $3$ of the $32$ different learned kernels of the model. Each corresponding to the OFF polarities and selective to the different motion directions (because of the symmetry observed between the ON and OFF event streams, we observed that kernels are very similar for the ON polarities). These weights are associated to a specific delay on the \textit{delays} axis and to a presynaptic address defined on the two other axes. %	For the sake of clarity, the values in range $[-0.05, 0.05]$ are not shown. 
        One sees positive (excitatory) coefficients for the specific direction of motion but also negative (inhibitory) coefficients for other directions.
	}
    \label{fig:kernels}
\end{figure*} 
%
%
After training our model, we first observe the weights learned for the different neurons (\seeFig{kernels}). Focusing on the positive weights, a strong selectivity is observed along specific axes for the different kernels. These directions can be easily associated to the direction of motion controlled in the natural images. For instance, the first kernel shows a selectivity to horizontal motion directions.
%
We observed a high dependendance between the weights reaching the ON polarities and that reaching the OFF polarities. ith the negative weights, one can observe an anti-selectivity for directions that do not correspond to the motion to which the kernel is selective to. This qualitative look at the 3D kernels allows the reader to infer for the $8$ different motion directions used to generate our synthetic event streams.

@@

%
\note{kernel size has to be adapted to the characteristics of motion see Samonds %~\citep{samonds}
say that we have tested }
\note{tester la meme expe faite par baudot et modelisée par kremkow}

>>>>

\subsection{Task definition: fast motion detection}
%%%-----------------------------------------------------------------
\note{c'est la meme expe faite par baudot et modelisée par kremkow}
Let us now define a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the field of vision. In animals with a fovea, this is particularly useful as it allows to move the area with the highest density of photoreceptors in the environment, for example at a point of interest. For example, saccades are rapid movements of the eyeball that reposition the center of vision. In humans, these are very frequent (on average one every 3 per second~\citep{dandekar_neural_2012}). They are produced very rapidly (about $80~\ms$) and display a whole range of speeds. At a more microscopic scale, the human gaze moves with an incessant drift similar to a Brownian-like trajectory~\citep{poletti_head-eye_2015}. To maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}. This approach first defines a finite set of possible 2D motions in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set of eye movements as the Cartesian product of N-V-phi=8 linearly spaced motion directions and N-Y-velocity=7 different velocities (see inset of \seeFig{motion_task}-(a)). Note that the velocities are sampled on a geometric scale between $1/4$ and $v-speed_base = 4$. Next, we define one trajectory of gaze as segments whose duration is drawn from a Poisson distribution with an average block length = $20~\ms$ - similar to a Lévy flight~\citep[p. 289]{mandelbrot_fractal_1982}. Finally, the trajectory is integrated by assuming 1/ that velocities are uniformly and independently sampled from the set of different motion-sets and 2/ that motion is uniform during a time segment. The resulting instances yield trajectories qualitatively similar to those observed for human eye movements (\seeFig{motion_task}-(a)). A similar procedure of animating of natural scene by virtual eye-movements was previously in neurobiliological~\citep{Baudot2013} and computational neuroscience~\citet{Kremkow2016} studies.

@@

Finally, the output of the MLR model is an event-based representation predicting at each position and at each time the probability of each motion. Such an output gives a form of optical flow that can be exploited for non-rigid motions, but we have defined here, for simplicity, an evaluation method that applies to our task with a full field motion. We have shown above that when different independent observations (here, the estimated motion at different spatial locations) are recognized as having a common cause (here, the rigid motion of the image), then an optimal estimate of the logit of this probability is the sum of the logits of the independent probabilities. By taking the logit of the probability of the output given by the model, we can therefore calculate the probability of the output. This allows one to calculate the accuracy (as the percentage of times the motion is accurately predicted) or the squared error $|| \speed - ||^2$ of the velocity estimate given by :
$
\speed = \sum_{\class} \speed_\class \cdot Pr(\class \vert image)
$ 
These calculations are performed on a different input dataset than the one used in the training or validation steps. These metrics will be useful to compare our methods with other methods on our defined task.  The complete code to reproduce the results of this paper is available at \url{https://github.com/SpikeAI/pyTERtorch}.  
\section{Results}
\label{sec:results}
%: fig:kernels
\subsection{Kernels learned for motion detection}
\begin{figure*}[ht!]
    {\centering
    %\vspace{-3cm}
    \includegraphics[width=\linewidth]{figures/motion_kernels.pdf}
    %\vspace{-.5cm}
    \caption{
    	Representation of the weights for $3$ of the $32$ different learned kernels of the model. Each corresponding to the OFF polarities and selective to the different motion directions (because of the symmetry observed between the ON and OFF event streams, we observed that kernels are very similar for the ON polarities). These weights are associated to a specific delay on the \textit{delays} axis and to a presynaptic address defined on the two other axes. %	For the sake of clarity, the values in range $[-0.05, 0.05]$ are not shown. 
        One sees positive (excitatory) coefficients for the specific direction of motion but also negative (inhibitory) coefficients for other directions.
    \label{fig:kernels}
\end{figure*} 
After training our model, we first analyze the weights learned for the different neurons (\seeFig{kernels}). 
We first observed a high dependendance between the weights reaching the ON polarities and that reaching the OFF polarities. In particular, whenever a weight for a given position and delay is positive for one poalrity, it will be negative in the other. This property comes from the way the events are generated and that the luminance can not at the same time increase and decrease. %ith the negative weights, one can observe an anti-selectivity for directions that do not correspond to the motion to which the kernel is selective to. 
We also observe that these cells show an orientation selectivity, similar to that observe in MT neurons~\citep{DeAngelis1999}. Interestingly, the relative organization of the receptive fields in quadrature of phase follows a push-pull organization predicted by~\citet{Kremkow2016} to explain neurophysiological results~\citep{Baudot2013}.  
Focusing on the positive weights, a strong selectivity is observed along specific axes of motion for each of the different kernels. These directions can be easily associated to the direction of motion controlled in the natural images. For instance, the first kernel shows a strong selectivity to horizontal motion directions.
%This qualitative look at the 3D kernels allows the reader to infer for the $8$ different motion directions used to generate our synthetic event streams.

@@

%
\note{kernel size has to be adapted to the characteristics of motion see Samonds %~\citep{samonds}
say that we have tested }
\note{tester la meme expe faite par baudot et modelisée par kremkow en montrant des raster plots du modele avec NI versus Gratings }
